### 2018-05-26 background.tex
Fix e.g. to e.g., and i.e. to i.e.,

In this blocked algorithm, the loops over the $N$, $K$ and $M$
matrix dimensions are tiled by sizes $N_c$, $K_c$ and $M_c$ at 
layers 1, 2 and 3, respectively.
At layers 4 and 5, the $N$ and $M$ dimensions are further tiled by sizes
$N_r$ and $M_r$, respectively.
As a result, the innermost loop at layer 6 goes over the $K$
dimension for a total of $K_c$ times,
with each iteration performing a rank-1 update on
the $M_r \times N_r$ sub-matrix of $C$, as shown at layer 7.
In OpenBLAS, matrix $C$ is scaled by $\beta$ before the loops,
so the multiply-accumulate operation at layer 7 does not have to scale $C$ again.
Tiling factors $N_c$, $K_c$, $M_c$, $N_r$ and $M_r$ are carefully selected so that
matrices on each level fit into a certain level in the memory hierarchy.
Equation~(\ref{eq:constraints.reg})--(\ref{eq:constraints.l3}) show
the constraints on these tiling factors.
$es$ denotes the size of matrix element, e.g. 8B for double precision floating-point numbers,
and $c_l$ denotes the capacity of registers or caches on level $l$.
First, by (\ref{eq:constraints.reg}), $M_r$ and $N_r$ are constrained that $M_r$ elements from $A$,
$N_r$ elements from $B$ and $M_r \times N_r$ elements from $C$ can fit into registers
(the pseudo level-0 cache).
Then, by (\ref{eq:constraints.l1}), $K_c$ is constrained that $B_4$ ($N_r \times K_c$),
$A_4$ ($M_r \times K_c$), and $A_4$'s counterpart in the next iteration
at layer 5 fit into the L1 cache.
Then, by (\ref{eq:constraints.l2}), $M_c$ is constrained that $A_3$ ($M_c \times K_c$),
$B_3$ ($N_r \times K_c$), and $B_3$'s counterpart in the next iteration
at layer 4 fit into the L2 cache.
At last, by (\ref{eq:constraints.l3}), $N_c$ is constrained that 
$B_2$ ($K_c \times N_c$) and $A_2$ ($M_c \times K_c$) fit into the L3 cache, if it exists.
Larger matrices on higher layers 1 -- 3 always reside in main memory.

@@

In contrary to intra-thread cache conflicts,
there exists another kind of cache conflicts,
inter-thread cache conflicts, on architectures with shared caches.
Suppose two working threads, $T_0$ and $T_1$, are running independently
on the 4-core processor in Figure.~\ref{fig:hierachy}
to accomplish a GEMM operation.
At time $t_s$, $T_0$ prefetches some data at address $addr_0$
to cache set $\varphi_2(addr_0)$ of the shared L2 cache.
The data will be actually read at time $t_e$.
Then at some time $t_m$ ($t_s < t_m < t_e$),
$T_1$ prefetches data at address $addr_1$ to L2 cache.
If $\varphi_2(addr_1)$ happens to be equal to $\varphi_2(addr_0)$,
data at $addr_1$ and $addr_0$ will be fetched to the same cache set.
As the shared L2 cache has a non-LRU policy,
data at $addr_0$ may suffer an eviction before it is actually read,
i.e. a conflict miss occurs.

>>>>

In this blocked algorithm, the loops over the $N$, $K$ and $M$
matrix dimensions are tiled by sizes $N_c$, $K_c$ and $M_c$ at 
layers 1, 2 and 3, respectively.
At layers 4 and 5, the $N$ and $M$ dimensions are further tiled by sizes
$N_r$ and $M_r$, respectively.
As a result, the innermost loop at layer 6 goes over the $K$
dimension for a total of $K_c$ times,
with each iteration performing a rank-1 update on
the $M_r \times N_r$ sub-matrix of $C$, as shown at layer 7.
In OpenBLAS, matrix $C$ is scaled by $\beta$ before the loops,
so the multiply-accumulate operation at layer 7 does not have to scale $C$ again.
Tiling factors $N_c$, $K_c$, $M_c$, $N_r$ and $M_r$ are carefully selected so that
matrices on each level fit into a certain level in the memory hierarchy.
Equation~(\ref{eq:constraints.reg})--(\ref{eq:constraints.l3}) show
the constraints on these tiling factors.
$es$ denotes the size of matrix element, e.g., 8B for double precision floating-point numbers,
and $c_l$ denotes the capacity of registers or caches on level $l$.
First, by (\ref{eq:constraints.reg}), $M_r$ and $N_r$ are constrained that $M_r$ elements from $A$,
$N_r$ elements from $B$ and $M_r \times N_r$ elements from $C$ can fit into registers
(the pseudo level-0 cache).
Then, by (\ref{eq:constraints.l1}), $K_c$ is constrained that $B_4$ ($N_r \times K_c$),
$A_4$ ($M_r \times K_c$), and $A_4$'s counterpart in the next iteration
at layer 5 fit into the L1 cache.
Then, by (\ref{eq:constraints.l2}), $M_c$ is constrained that $A_3$ ($M_c \times K_c$),
$B_3$ ($N_r \times K_c$), and $B_3$'s counterpart in the next iteration
at layer 4 fit into the L2 cache.
At last, by (\ref{eq:constraints.l3}), $N_c$ is constrained that 
$B_2$ ($K_c \times N_c$) and $A_2$ ($M_c \times K_c$) fit into the L3 cache, if it exists.
Larger matrices on higher layers 1 -- 3 always reside in main memory.

@@

In contrary to intra-thread cache conflicts,
there exists another kind of cache conflicts,
inter-thread cache conflicts, on architectures with shared caches.
Suppose two working threads, $T_0$ and $T_1$, are running independently
on the 4-core processor in Figure.~\ref{fig:hierachy}
to accomplish a GEMM operation.
At time $t_s$, $T_0$ prefetches some data at address $addr_0$
to cache set $\varphi_2(addr_0)$ of the shared L2 cache.
The data will be actually read at time $t_e$.
Then at some time $t_m$ ($t_s < t_m < t_e$),
$T_1$ prefetches data at address $addr_1$ to L2 cache.
If $\varphi_2(addr_1)$ happens to be equal to $\varphi_2(addr_0)$,
data at $addr_1$ and $addr_0$ will be fetched to the same cache set.
As the shared L2 cache has a non-LRU policy,
data at $addr_0$ may suffer an eviction before it is actually read,
i.e., a conflict miss occurs.

### 2018-05-26 evaluation.tex
Fix e.g. to e.g., and i.e. to i.e.,

All evaluations run with the same tiling factors
$M_r$, $N_r$, $K_c$, $M_c$ and $N_c$.
The tiling factors are computed as in Section~\ref{subsec:example},
i.e. $M_r = 4$, $N_r = 8$, $K_c = 256$, $M_c = 192$, $N_c = 1024NT$.
The parallelism is controlled by two parameters,
the number of active clusters $NC$,
and the number of active threads per cluster $NT_C$.
The total number of threads is $NT = NC \cdot NT_C$.
For the Phytium 2000+ processor, the valid ranges for $NC$ and $NT_C$
are $NC \in [1, 16]$ and $NT_C \in [1, 4]$, respectively.
Generally, DGEMM performance is presented in $flops$.
%% floating-point operations per second ($flops$).
As $NT$ varies in our evaluation,
we use another metric derived from $flops$,
the average thread efficiency,
to present performance results consistently.
The average thread efficiency is a normalized value computed as
$E_{avg} = flops / (NT \cdot \widehat{flops})$
in which $\widehat{flops}$ stands for the theoretical performance peak of a single core.
%% \begin{equation*}
%%   E = flops / (NT \cdot \widehat{flops})
%% \end{equation*}

@@

Privatization introduces more packing overhead because
redundant packing of $B_2$ is enforced.
Figure.~\ref{fig:packb} shows three packing strategies for $B_2$
in a parallelism configuration $NT_C=4$ and $NC=4$.
The whole packing workload of $B_2$ is divided into 16 tasks
and the packing workload of thread $T_1$ is masked by z-curves. 
%% and the task assignment is annoted in Figure.~\ref{fig:packb}.
In conventional packing, each thread takes a single task.
In full privatization, all tasks are replicated to all threads.
As a result, the packing overhead grows in proportion to $NT$
in full privatization strategy, which is unacceptable
if GEMM is highly parallelized, e.g. $NT=64$.
Partial privatization in Figure.~\ref{fig:packb.partial}
offers an alternative to full privatization.
In partial privatization, privatization only occurs inside
a cluster so that tasks belong to one cluster need not to be
replicated to other clusters.
Consequently, extra packing overhead of the partial privatization
strategy is bounded by $NT_C$.
For instance, on Phytium 2000+, overhead of packing $B_2$
in partial privatization is limited to 4 times
of that in conventional packing.

>>>>

All evaluations run with the same tiling factors
$M_r$, $N_r$, $K_c$, $M_c$ and $N_c$.
The tiling factors are computed as in Section~\ref{subsec:example},
i.e., $M_r = 4$, $N_r = 8$, $K_c = 256$, $M_c = 192$, $N_c = 1024NT$.
The parallelism is controlled by two parameters,
the number of active clusters $NC$,
and the number of active threads per cluster $NT_C$.
The total number of threads is $NT = NC \cdot NT_C$.
For the Phytium 2000+ processor, the valid ranges for $NC$ and $NT_C$
are $NC \in [1, 16]$ and $NT_C \in [1, 4]$, respectively.
Generally, DGEMM performance is presented in $flops$.
%% floating-point operations per second ($flops$).
As $NT$ varies in our evaluation,
we use another metric derived from $flops$,
the average thread efficiency,
to present performance results consistently.
The average thread efficiency is a normalized value computed as
$E_{avg} = flops / (NT \cdot \widehat{flops})$
in which $\widehat{flops}$ stands for the theoretical performance peak of a single core.
%% \begin{equation*}
%%   E = flops / (NT \cdot \widehat{flops})
%% \end{equation*}

@@

Privatization introduces more packing overhead because
redundant packing of $B_2$ is enforced.
Figure.~\ref{fig:packb} shows three packing strategies for $B_2$
in a parallelism configuration $NT_C=4$ and $NC=4$.
The whole packing workload of $B_2$ is divided into 16 tasks
and the packing workload of thread $T_1$ is masked by z-curves. 
%% and the task assignment is annoted in Figure.~\ref{fig:packb}.
In conventional packing, each thread takes a single task.
In full privatization, all tasks are replicated to all threads.
As a result, the packing overhead grows in proportion to $NT$
in full privatization strategy, which is unacceptable
if GEMM is highly parallelized, e.g., $NT=64$.
Partial privatization in Figure.~\ref{fig:packb.partial}
offers an alternative to full privatization.
In partial privatization, privatization only occurs inside
a cluster so that tasks belong to one cluster need not to be
replicated to other clusters.
Consequently, extra packing overhead of the partial privatization
strategy is bounded by $NT_C$.
For instance, on Phytium 2000+, overhead of packing $B_2$
in partial privatization is limited to 4 times
of that in conventional packing.

### 2018-05-26 intro.tex
Fix e.g. to e.g., and i.e. to i.e.,

\section{Introduction}\label{sec:intro}
Dense linear algebra libraries are the most fundamental software in
scientific and engineering computing domains.
Basic Linear Algebra Subprograms (BLAS) (FIXME) defines a collection
of APIs which act as standard building blocks for dense matrix operations.
BLAS routines are divided into 3 levels,
level-1 for vector-vector operations,
level-2 for matrix-vector operations,
and level-3 for matrix-matrix operations.
Processor vendors often provide BLAS implementations
highly optimized for their processors,
such as Intel MKL, AMD ACML and NVIDIA cuBLAS.
The HPC community has also contributed several high-quality
BLAS implementations, e.g. ATLAS~\cite{atlas},
GotoBLAS~\cite{gotoblas}, OpenBLAS~\cite{openblas},
and BLIS~\cite{blis,blisport}.

@@

The software prefetching and data packing approach meet a challenge
when working on architectures with non-LRU shared caches.
In traditional high-performance processors, e.g. the Intel Xeon series,
both L1 and L2 caches are private to processor cores
and LRU replacement policy is adopted.
Without considering the last level cache (LLC),
threads running on different cores prefetch their data into
different caches, and private data of different threads
cannot cause conflict cache misses.
This is not the case if caches are shared by several processor cores.
There are chances that a cache line prefetched by one thread
get evicted out before its lifetime ends because another thread prefetches
another cache line into the same cache set.
A simple solution would be shrinking the size of packed matrix
so data used by several threads can simultaneously reside in the shared cache.
Due to the nature of set-associative caches,
this solution cannot completely eliminate inter-thread cache conflicts,
especially if the shared cache has a non-LRU replacement policy.
Evaluation results show that inter-thread cache conflicts on non-LRU shared caches
can heavily hurt GEMM performance,
even with packed matrices shrinked to fit into the cache.

>>>>

\section{Introduction}\label{sec:intro}
Dense linear algebra libraries are the most fundamental software in
scientific and engineering computing domains.
Basic Linear Algebra Subprograms (BLAS) (FIXME) defines a collection
of APIs which act as standard building blocks for dense matrix operations.
BLAS routines are divided into 3 levels,
level-1 for vector-vector operations,
level-2 for matrix-vector operations,
and level-3 for matrix-matrix operations.
Processor vendors often provide BLAS implementations
highly optimized for their processors,
such as Intel MKL, AMD ACML and NVIDIA cuBLAS.
The HPC community has also contributed several high-quality
BLAS implementations, e.g., ATLAS~\cite{atlas},
GotoBLAS~\cite{gotoblas}, OpenBLAS~\cite{openblas},
and BLIS~\cite{blis,blisport}.

@@

The software prefetching and data packing approach meet a challenge
when working on architectures with non-LRU shared caches.
In traditional high-performance processors, e.g., the Intel Xeon series,
both L1 and L2 caches are private to processor cores
and LRU replacement policy is adopted.
Without considering the last level cache (LLC),
threads running on different cores prefetch their data into
different caches, and private data of different threads
cannot cause conflict cache misses.
This is not the case if caches are shared by several processor cores.
There are chances that a cache line prefetched by one thread
get evicted out before its lifetime ends because another thread prefetches
another cache line into the same cache set.
A simple solution would be shrinking the size of packed matrix
so data used by several threads can simultaneously reside in the shared cache.
Due to the nature of set-associative caches,
this solution cannot completely eliminate inter-thread cache conflicts,
especially if the shared cache has a non-LRU replacement policy.
Evaluation results show that inter-thread cache conflicts on non-LRU shared caches
can heavily hurt GEMM performance,
even with packed matrices shrinked to fit into the cache.

### 2018-05-26 scp.tex
Fix e.g. to e.g., and i.e. to i.e.,

Suppose we are implementing a double precision GEMM (DGEMM) on
the 4-core processor, i.e. $es=8B$.
We now determine the tiling factors used in DGEMM following the procedure described
by constraints (\ref{eq:constraints.reg})--(\ref{eq:constraints.l3}).
Various configurations for ($M_r$, $N_r$) can satisfy (\ref{eq:constraints.reg}),
e.g. $(4,8)$, $(8,4)$, $(6,8)$, and $(8,6)$. 
It takes careful consideration to determine which one is the best,
and a tuning process may be needed.
After tuning we obtain the best values $M_r = 4$ and $N_r = 8$.
By (\ref{eq:constraints.l1}),
$K_c \le \lfloor c_{L1}/es/nt_{L1}/(N_r + 2 M_r) \rfloor = \lfloor 32KB/8B/1/16 \rfloor = 256$.
Here we choose $K_c=256$.
By (\ref{eq:constraints.l2}),
$M_c \le \lfloor (c_{L2}/es/nt_{L2} - 2 N_r K_c )/ K_c \rfloor =
\lfloor (2MB/8B/4 - 2*8*256)/256 \rfloor = 240$.
To leave space for other data structures, as well as the program code,
it is reasonable to shrink $M_c$ to a slightly smaller value,
e.g. $192$, $208$ and $224$ are all proper candidates for $M_c$.
Similar to $M_r$ and $N_r$, a tuning process may be needed to
find the best value for $M_c$.
Here we choose $M_c = 192$.
As there is no L3 cache, (\ref{eq:constraints.l3}) can be ignored
and $N_c$ can be given a large value.
Here we choose $N_c = 1024NT = 4096$.
With tiling factors determined, the sizes of packed matrices
can be calculated. Table.~\ref{tab:msizes} list the sizes of
various packed matrices.

@@

Before diving into details, we make a few assumptions,
which are standard practice rarely violated,
on the architectures that SCP can deal with:
\begin{itemize}
\item The architecture has 2 or 3 levels of cache. %% i.e. $NL=2$ or $NL=3$
\item All caches are inclusive set-associative caches. %% i.e. $n_l \ge 2$ for $l \in [1, NL]$
\item Caches on the same level are homogeneous. %% i.e. $L_l^i = L_l^j$ for $i \ne j$, $l \in [1, NL]$.
\item A cache's way-capacity is a multiple of the sum of way-capacity of its children,
i.e. $(\frac{nt_l}{nt_{l-1}} \cdot wc_{l-1}) \mid wc_l$.
\end{itemize}

We use a memory descriptor $\mathcal{D}_t^M$ to specify 
the memory space occupied by packed matrix $M$ used by thread $t$.
The memory descriptor is essentially a subspace of
the whole address space, i.e. $\mathcal{D}_t^M \subset \mathcal{A}$.
%% The memory layout of a packed matrix is described by a memory descriptor,
%% which is essentially a subspace of the whole address space $\mathcal{A}$.
%% Each packed matrix $M$ used by thread $t$,
%% is associated with a memory descriptor $\mathcal{D}_t^M$
%% specifying the memory space it occupies.
Generally, $\mathcal{D}_t^M$ consists of a sequence of $N_t^M$ disjoint memory segments,
$\mathcal{D}_t^M = \{ S_0, S_1, \cdots, S_{N_t^M}\}$.
%% in which $S_i \bigcap S_j = \phi$ if $i \ne j$.
A segment is represented by its start and end addresses $S_i = [s_i, e_i)$,
in which $s_i < e_i \in \mathcal{A}$.
With way-partitioning, the memory descriptor contains only one segment.
With set-partitioning used in previous section,
the memory descriptor contains a sequence of equally strided segments.

@@

SCP runs in three phases.
The first phase allocates memory buffers for all $A_2$ and $B_2$
instances used in GEMM. There are two buffers, $\mathcal{D}_p$ and $\mathcal{D}_s$,
for storing private and shared matrices respectively.
The second phase computes memory descriptors for $A_2$ instances
by partitioning $\mathcal{D}_p$ into $NT$ thread-private buffers
$\mathcal{D}_t^{A_2}$ , $t \in [0, NT)$.
Buffers of different threads are disjoint,
i.e. $\mathcal{D}_i^{A_2} \bigcap \mathcal{D}_j^{A_2} = \phi$ if $i \ne j$.
The third phase computes memory descriptors for $B_2$.
Because is $B_2$ is shared among all threads,
$\mathcal{D}_t^{B_2}$ does not represent the whole $B_2$ matrix,
but the part (of size $\frac{es N_c K_c}{NT}$) which is packed by thread $t$.
The working flow of these three phases is listed
in Algorithm~\ref{alg:scp.phase1} -- \ref{alg:scp.phase3}.

@@

%% FIXME memory buffer? memory space? subspace?
Algorithm~\ref{alg:scp.phase2} shows the second phase of SCP.
The main part is a recursive procedure $subspace$
(line~\ref{line:subspace.begin}--\ref{line:subspace.end}).
The $subspace$ procedure traverses the memory hierarchy
to compute for each node, including the processor cores and main memory,
a subspace of $\mathcal{D}_p$.
$subspace$ has three input parameters, $l$ and $idx$ to
identify the node on which it is running,
and a subspace $\mathcal{D}_l^{idx} \subset \mathcal{D}_p$ allocated to the node. 
The functionality of $subspace$ is to partition $\mathcal{D}_l^{idx}$
among all children of node $(l, idx)$.
If $subspace$ encounters a level 0 node, i.e. a processor core,
then $\mathcal{D}_l^{idx}$ is exactly the thread-private
memory buffer $\mathcal{D}_{idx}$ for thread $idx$ and $subspace$ returns early
(line~\ref{line:shortcut.begin}--\ref{line:shortcut.end}).
If this is not the case, the number of children is computed (line~\ref{line:nchildren})
and $subspace$ iterates over all the child nodes
(line~\ref{line:for.begin}--\ref{line:for.end}).
For each child node $cidx$ on layer $l-1$ (line~\ref{line:cidx}),
its memory space $\mathcal{D}_{l-1}^{cidx}$ is computed
and $subspace$ is called recursively on it (line~\ref{line:recursive}).
$\mathcal{D}_{l-1}^{cidx} \subset \mathcal{D}_l^{idx}$ is obtained
by intersecting $\mathcal{D}_l^{idx}$ with
a temporal memory space $\mathcal{D}_{temp}$ (line~\ref{line:childspace}).
The if-else branches (line~\ref{line:if}--\ref{line:endif})
show two distinct ways to compute $\mathcal{D}_{temp}$.
If the node is main memory or a LRU cache (line~\ref{line:if}),
$\mathcal{D}_l^{idx}$ is partitioned in the conventional
way-partitioning style.
Otherwise, the else branch (line~\ref{line:else}) performs
a set-partitioning on $\mathcal{D}_l^{idx}$.
Initially, the main memory gets the whole $\mathcal{D}_p$ (line~\ref{line:memory.d})
and $nt_{NL+1}$ is set to $NT$ (line~\ref{line:memory.nt})
because the main memory is shared by all threads.
Then $subspace$ procedure starts from the main memory (line~\ref{line:subspace.root})
and traverses the memory hierarchy in a depth-first-search order.

>>>>

Suppose we are implementing a double precision GEMM (DGEMM) on
the 4-core processor, i.e., $es=8B$.
We now determine the tiling factors used in DGEMM following the procedure described
by constraints (\ref{eq:constraints.reg})--(\ref{eq:constraints.l3}).
Various configurations for ($M_r$, $N_r$) can satisfy (\ref{eq:constraints.reg}),
e.g., $(4,8)$, $(8,4)$, $(6,8)$, and $(8,6)$. 
It takes careful consideration to determine which one is the best,
and a tuning process may be needed.
After tuning we obtain the best values $M_r = 4$ and $N_r = 8$.
By (\ref{eq:constraints.l1}),
$K_c \le \lfloor c_{L1}/es/nt_{L1}/(N_r + 2 M_r) \rfloor = \lfloor 32KB/8B/1/16 \rfloor = 256$.
Here we choose $K_c=256$.
By (\ref{eq:constraints.l2}),
$M_c \le \lfloor (c_{L2}/es/nt_{L2} - 2 N_r K_c )/ K_c \rfloor =
\lfloor (2MB/8B/4 - 2*8*256)/256 \rfloor = 240$.
To leave space for other data structures, as well as the program code,
it is reasonable to shrink $M_c$ to a slightly smaller value,
e.g., $192$, $208$ and $224$ are all proper candidates for $M_c$.
Similar to $M_r$ and $N_r$, a tuning process may be needed to
find the best value for $M_c$.
Here we choose $M_c = 192$.
As there is no L3 cache, (\ref{eq:constraints.l3}) can be ignored
and $N_c$ can be given a large value.
Here we choose $N_c = 1024NT = 4096$.
With tiling factors determined, the sizes of packed matrices
can be calculated. Table.~\ref{tab:msizes} list the sizes of
various packed matrices.

@@

Before diving into details, we make a few assumptions,
which are standard practice rarely violated,
on the architectures that SCP can deal with:
\begin{itemize}
\item The architecture has 2 or 3 levels of cache. %% i.e., $NL=2$ or $NL=3$
\item All caches are inclusive set-associative caches. %% i.e., $n_l \ge 2$ for $l \in [1, NL]$
\item Caches on the same level are homogeneous. %% i.e., $L_l^i = L_l^j$ for $i \ne j$, $l \in [1, NL]$.
\item A cache's way-capacity is a multiple of the sum of way-capacity of its children,
i.e., $(\frac{nt_l}{nt_{l-1}} \cdot wc_{l-1}) \mid wc_l$.
\end{itemize}

We use a memory descriptor $\mathcal{D}_t^M$ to specify 
the memory space occupied by packed matrix $M$ used by thread $t$.
The memory descriptor is essentially a subspace of
the whole address space, i.e., $\mathcal{D}_t^M \subset \mathcal{A}$.
%% The memory layout of a packed matrix is described by a memory descriptor,
%% which is essentially a subspace of the whole address space $\mathcal{A}$.
%% Each packed matrix $M$ used by thread $t$,
%% is associated with a memory descriptor $\mathcal{D}_t^M$
%% specifying the memory space it occupies.
Generally, $\mathcal{D}_t^M$ consists of a sequence of $N_t^M$ disjoint memory segments,
$\mathcal{D}_t^M = \{ S_0, S_1, \cdots, S_{N_t^M}\}$.
%% in which $S_i \bigcap S_j = \phi$ if $i \ne j$.
A segment is represented by its start and end addresses $S_i = [s_i, e_i)$,
in which $s_i < e_i \in \mathcal{A}$.
With way-partitioning, the memory descriptor contains only one segment.
With set-partitioning used in previous section,
the memory descriptor contains a sequence of equally strided segments.

@@

SCP runs in three phases.
The first phase allocates memory buffers for all $A_2$ and $B_2$
instances used in GEMM. There are two buffers, $\mathcal{D}_p$ and $\mathcal{D}_s$,
for storing private and shared matrices respectively.
The second phase computes memory descriptors for $A_2$ instances
by partitioning $\mathcal{D}_p$ into $NT$ thread-private buffers
$\mathcal{D}_t^{A_2}$ , $t \in [0, NT)$.
Buffers of different threads are disjoint,
i.e., $\mathcal{D}_i^{A_2} \bigcap \mathcal{D}_j^{A_2} = \phi$ if $i \ne j$.
The third phase computes memory descriptors for $B_2$.
Because is $B_2$ is shared among all threads,
$\mathcal{D}_t^{B_2}$ does not represent the whole $B_2$ matrix,
but the part (of size $\frac{es N_c K_c}{NT}$) which is packed by thread $t$.
The working flow of these three phases is listed
in Algorithm~\ref{alg:scp.phase1} -- \ref{alg:scp.phase3}.

@@

%% FIXME memory buffer? memory space? subspace?
Algorithm~\ref{alg:scp.phase2} shows the second phase of SCP.
The main part is a recursive procedure $subspace$
(line~\ref{line:subspace.begin}--\ref{line:subspace.end}).
The $subspace$ procedure traverses the memory hierarchy
to compute for each node, including the processor cores and main memory,
a subspace of $\mathcal{D}_p$.
$subspace$ has three input parameters, $l$ and $idx$ to
identify the node on which it is running,
and a subspace $\mathcal{D}_l^{idx} \subset \mathcal{D}_p$ allocated to the node. 
The functionality of $subspace$ is to partition $\mathcal{D}_l^{idx}$
among all children of node $(l, idx)$.
If $subspace$ encounters a level 0 node, i.e., a processor core,
then $\mathcal{D}_l^{idx}$ is exactly the thread-private
memory buffer $\mathcal{D}_{idx}$ for thread $idx$ and $subspace$ returns early
(line~\ref{line:shortcut.begin}--\ref{line:shortcut.end}).
If this is not the case, the number of children is computed (line~\ref{line:nchildren})
and $subspace$ iterates over all the child nodes
(line~\ref{line:for.begin}--\ref{line:for.end}).
For each child node $cidx$ on layer $l-1$ (line~\ref{line:cidx}),
its memory space $\mathcal{D}_{l-1}^{cidx}$ is computed
and $subspace$ is called recursively on it (line~\ref{line:recursive}).
$\mathcal{D}_{l-1}^{cidx} \subset \mathcal{D}_l^{idx}$ is obtained
by intersecting $\mathcal{D}_l^{idx}$ with
a temporal memory space $\mathcal{D}_{temp}$ (line~\ref{line:childspace}).
The if-else branches (line~\ref{line:if}--\ref{line:endif})
show two distinct ways to compute $\mathcal{D}_{temp}$.
If the node is main memory or a LRU cache (line~\ref{line:if}),
$\mathcal{D}_l^{idx}$ is partitioned in the conventional
way-partitioning style.
Otherwise, the else branch (line~\ref{line:else}) performs
a set-partitioning on $\mathcal{D}_l^{idx}$.
Initially, the main memory gets the whole $\mathcal{D}_p$ (line~\ref{line:memory.d})
and $nt_{NL+1}$ is set to $NT$ (line~\ref{line:memory.nt})
because the main memory is shared by all threads.
Then $subspace$ procedure starts from the main memory (line~\ref{line:subspace.root})
and traverses the memory hierarchy in a depth-first-search order.
